Fast, Scalable Phrase-Based SMT Decoding

### 2016-01-29 acl.2016/acl2016.tex
acl paper

We trained two phrase-based systems using the Moses toolkit, with standard settings. The first system was trained on most of the publicly available Arabic-English data from Opus (Jörg Tiedemann, 2012,) consisting of over 69 million parallel sentences, and tuned on a held out set. The second system was trained on the French-English Europarl corpus. The phrase-tables were then pruned, keeping only the top 100 entries per source phrase, according to $p(t|s)$. All models files were then binarized; thelanguage models were binaized using KenLM (???), the phrase table using Probing PT (???), lexicalized reordering model using the compact datastructure described in ???. These binary formats were choosen for their best-of-class multithreaded performance. Table~\ref{tab:model-files} gives details of the resultant sizes of the model files.
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
Phrase table  	& 17 	& 5.8 \\
Language model 	& 3.1  	& 1.8 \\ 
Lex-re model	& 2.3	& 637MB \\ \hline
\end{tabular}
\end{center}
\caption{Model sizes in GB}
\label{tab:model-files}
\end{table}

For testing decoding speed, we used a subset of the training data, Table~\ref{tab:test-sets}. The two test set have differing characterics that we are interested in analyzing, ar-en have short sentences while fr-en have overly long sentences.

@@

Over 30\% of the Moses decoder running time is spent on memory management and this increases when more threads are used, Table~\ref{tab:optimizing-memory}. By contrast, our decoder spends ???\% on memory management.
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& 1 thread	& 32 threads \\ \hline
Moses  		& ???\% 	& ???\% \\
Our work 	& ???\% 	& ???\% \\ \hline
\end{tabular}
\end{center}
\caption{\%age decoding time managing memory}
\label{tab:optimizing-memory}
\end{table}

A potential disadvantage of using memory pool is that the decoder will use more memory, however, Table~\ref{tab:memory-usage} shows that peak memory consumption are comparable.
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& 1 thread	& 32 threads \\ \hline
Moses  		& ???	 	& ??? \\
Our work 	& ??? 		& ??? \\ \hline
\end{tabular}
\end{center}
\caption{Peak Memory Usage in GB}
\label{tab:memory-usage}
\end{table}

>>>>

We trained a phrase-based system using the Moses toolkit with standard settings. The training data consisted of most of the publicly available Arabic-English data from Opus (Jörg Tiedemann, 2012,) containing over 69 million parallel sentences, and tuned on a held out set. The phrase-table was then pruned, keeping only the top 100 entries per source phrase, according to $p(t|s)$. All models files were then binarized; the language models were binaized using KenLM (???), the phrase table using Probing PT (???), lexicalized reordering model using the compact datastructure described in ???. These binary formats were choosen for their best-of-class multithreaded performance. Table~\ref{tab:model-files} gives details of the resultant sizes of the model files. For verification with a different dataset, we also used a second system trained on the French-English Europarl corpus. 
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
Phrase table  	& 17 	& 5.8 \\
Language model 	& 3.1  	& 1.8 \\ 
Lex-re model	& 2.3	& 637MB \\ \hline
\end{tabular}
\end{center}
\caption{Model sizes in GB}
\label{tab:model-files}
\end{table}
For testing decoding speed, we used a subset of the training data, Table~\ref{tab:test-sets}. The two test set have differing characterics that we are interested in analyzing, ar-en have short sentences while fr-en have overly long sentences.

@@

Over 24\% of the Moses decoder running time is spent on memory management and this increases when more threads are used, Table~\ref{tab:optimizing-memory}, braking the scaling of the decoder to many cores. By contrast, our decoder spends 11\% on memory management and does not significantly increase with more cores.
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|c|c|} \hline
		& \multicolumn{2}{c|} {Moses}	& \multicolumn{2}{c|} {Our Work} \\ \hline
\# threads	& 1 		& 32	& 1 		& 32  \\ \hline
Memory  	& 24		& 39 	& 11		& 13 \\
LM 		& 12	 	& 2 	& 47		& 38 \\ 
Phrase-table	& 9	 	& 5 	& 2		& 4 \\ 
Lex RO 		& 8	 	& 2 	& 2		& 2 \\ 
Search 		& 2	 	& 0 	& 14		& 19 \\ 
Misc/Unknown	& 45	 	& 39 	& 24		& 29 \\ \hline
\end{tabular}
\end{center}
\caption{Profile of \%age decoding time}
\label{tab:optimizing-memory}
\end{table}

% A potential disadvantage of using memory pool is that the decoder will use more memory, however, Table~\ref{tab:memory-usage} shows that peak memory consumption are comparable.
% \begin{table}[h]
% \begin{center}
% \begin{tabular}{|l|c|c|} \hline
% 		& 1 thread	& 32 threads \\ \hline
% Moses  		& ???	 	& ??? \\
% Our work 	& ??? 		& ??? \\ \hline
% \end{tabular}
% \end{center}
% \caption{Peak Memory Usage in GB}
% \label{tab:memory-usage}
% \end{table}
